|

### 2021-03-17 documentation/paper.Rmd
Updated model to deal with errant end points and recompiled

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, Y, and Z. We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

>>>>

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback. We would also like to thank X, Y, and Z for offering their time to review the manuscript. Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

### 2021-03-17 documentation/readme.Rmd
Amended README text
Updated model to deal with errant end points and recompiled

`britpol` is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/britpol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/britpol/blob/master/download/paper.pdf).

To install the latest version of `britpol`, run the following code in `R`:

``` r
devtools::install_github("jackobailey/britpol")
```

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. [Click here to download them](https://github.com/jackobailey/britpol/tree/master/download).

## Latest Polling Estimates

@@

As of `r str_remove(format(Sys.Date(), "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote. **In third place is the `r txt_dta$party[3]`**, with support from `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.

@@

Both `pollbase` and `pollbasepro` are living datasets. As such, users should try to use only the most recent version of the data when conducting their analyses. Like any project of this size, some minor mistakes might have crept into the data processing pipeline. If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).

Your may use the `britpol` codebase for your own purposes, but you must do so *with attribution*. That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used britpol to produce your work. The citations for each item in `britpol` are as follows:

>>>>

`{britpol}` is an `R` package that makes analysing British political data quick and simple. It contains two pre-formatted datasets, plus a host of useful functions. The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia. The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. [Stata and SPSS versions of the data are also available too](https://github.com/jackobailey/britpol/tree/master/download).

To install the latest version of `{britpol}`, run the following code in `R`:

``` r
devtools::install_github("jackobailey/britpol")

## Latest Polling Estimates from PollBasePro

@@

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** at around `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote. **The `r txt_dta$party[3]` are in third place** with support from `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.

@@

{britpol}, `pollbase`, and `pollbasepro` will change over time as elections come and go. Users should use only the most recent version of the package when conducting their analyses. Like any project, some minor mistakes might have crept into the code. If you think that you have found an error or would like to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).

You may also use the `{britpol}` codebase for your own purposes in line with our license. But you must do so *with attribution*. That is, you may reproduce, reuse, and adapt the code as you see fit, but must state in each case that you used `{britpol}` to produce your work. The relevant citations are as follows:
